---
title: "battletech.ELUARD"
author: "Manon Eluard"
format: html
editor: visual
github-repository : https://github.com/manoneld/battletech.git
---

#### R configuration

```{r}
#| echo: false 
#| message: false
library(here)
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(vroom)
library(stringr)
here::i_am("battletech.Rproj")
```

### Data Loading : question 3 

``````{r}
#| message: false
database <- vroom(here("data","star+systems.csv"), 
                  delim = ":", 
                  na = c("Unknown", "NA"), 
                  quote = "\"")
```

The number of observations is  `r nrow(database)` described by `r ncol(database)` variables

```{r}
star_name <- database$"STAR_NAME"
class(star_name) #character

distance <- database$"DISTANCE (LIGHTYEARS)"
class(distance) #numeric (check verified)

stellar_type <- database$"stellar type"
class(stellar_type) #character 

star_idx <- database$"star_idx"
class(star_idx)

temperature <- database$ "EQUIVALENT TEMPERATURE"
class(temperature)

radius <- database$"STAR RADIUS"
class(radius)
  
mass <- database$"RELATIVE MASS"
class(mass)

luminosity <- database$"Luminosity"
class(luminosity)
```

### Question 4 

```{r}
n_obs <- database |> count(nrow(database))
n_obs
n_variables <- database |> count(ncol(database))
n_variables
miss_values <- summarise_all(database, ~sum(is.na(.)))
miss_values
obs_one_miss_val <- sum(rowSums(is.na(database)) > 0)
obs_one_miss_val

kable(list(n_obs, n_variables, miss_values, obs_one_miss_val), caption = "Summary Statistics")

```


